---
title: "BACS HW16"
author: '109077446'
date: "6/10/2021"
output: word_document
---

```{r}
library(seminr)
security_data_sem = read.csv("security_data_sem.csv")
```

##        *Question #1 - Composite Path Models*

##            a-i) Measurement Model

```{r}
sec_measurement_model <- constructs(
  composite("TRUST", multi_items('TRST',1:4)),
  composite("SEC", multi_items('PSEC',1:4)),
  composite("REP", multi_items('PREP',1:4)),
  composite("INV", multi_items('PINV',1:3)),
  composite("POL", multi_items('PPSS',1:3)),
  composite("FAML", single_item('FAML1')),
  interaction_term(iv = 'REP', moderator = 'POL', method = orthogonal)
)
```

##            a-ii) Structural Model

```{r}
sec_structural_model <- relationships(
  paths(from = c("REP","INV","POL", "FAML", "REP*POL"), to = "SEC"),
  paths(from = "SEC", to = "TRUST")
  
)

sec_pls <- estimate_pls(data = security_data_sem, measurement_model = sec_measurement_model, structural_model = sec_structural_model)

```

##            b-1) Plot a figure of the estimated model

```{r}

library("DiagrammeR")
plot(sec_pls, title="PLS")
```

```{r}
sec_pls_sum <- summary(sec_pls)
```


##            b-ii) Weights and loadings of composites

```{r}
sec_pls_sum$weights

## WEIGHTS
```

```{r}
sec_pls_sum$loadings

##LOADINGS
```


##            b-iii) Regression coefficients of paths between factors

```{r}
sec_pls_sum$paths
```


##            b-iv) Bootstrapped path coefficients: t-values, 95% CI

```{r}
boot_pls <- bootstrap_model(sec_pls, nboot= 1000)

summary(boot_pls)
```


##            *Question #2 - Create a common factor model using SEMinR*

##                a-i)Either respecify all the constructs as being reflective(),

```{r}
cfm_model <-constructs( 
  reflective('TRUST', multi_items('TRST', 1:4)),
  reflective('SEC', multi_items('PSEC', 1:4)),
  reflective('REP', multi_items('PREP', 1:4)),
  reflective('INV', multi_items('PINV', 1:3)),
  reflective('POL', multi_items('PPSS', 1:3)),
  reflective('FAML', single_item('FAML1')),
  interaction_term(iv='REP', moderator='POL', method=orthogonal) 
  )
```

##                a-ii) Use the same structural model as before

```{r}
cfm_structure <- relationships(
  paths(from = c("REP","INV","POL", "FAML", "REP*POL"), to = "SEC"),
  paths(from = "SEC", to = "TRUST")
  
)
```


##                b-i) Plot a figure of the estimated model

```{r}
library(seminr)
cfm_pls <- estimate_cbsem(data = security_data_sem, measurement_model = cfm_model, structural_model = cfm_structure)


plot(cfm_pls, title="Common-Factor Models using CB-SEM")
```

##              b-ii) Loadings of composites

```{r}
cfm_pls_report <- summary(cfm_pls)
cfm_pls_report$loadings

```
##                b-iii) Regression coefficients of paths between factors, and their p-values

```{r}
cfm_pls_report$paths
```
