---
title: "Cars_Model REgression"
author: '109077446'
date: "12/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

In this script I will be working on the following points: 

 1- Produce the last regression model by using the Cars data 
 2- Run the Regression
 3- Bootstrap the original dataset
 4- Mean centered the outcome, bootstrap it and see what the coefficient looks like.
 5- plot the coefficient 
 6- The density plot of the coefficient
 
 
 ## Produce the last regression model 
 
```{r}
cars <- read.table("auto-data.txt", header=FALSE, na.strings = "?")
names(cars) <- c("mpg", "cylinders", "displacement", "horsepower", "weight",
"acceleration", "model_year", "origin", "car_name")
cars_log <- with(cars, data.frame(log(mpg), log(cylinders), log(displacement), log(horsepower), log(weight), log(acceleration), model_year, origin))

```

```{r}
cars_log_regr<- lm(log.mpg. ~ log.cylinders.+log.displacement.+log.horsepower.+log.weight.+log.acceleration.+model_year+factor(origin),data=cars_log)
summary(cars_log_regr)
```

#Bootstrap the original dataset

```{r}


plot(log(cars$weight), log(cars$mpg), col=NA, pch=19, main="Bootstrapped Confidence Intervals")
boot_regr <- function(model, dataset) {
 boot_index <- sample(1:nrow(dataset), replace=TRUE)
 data_boot <- dataset[boot_index,]
 regr_boot <- lm(model, data=data_boot)
 abline(regr_boot, lwd=1, col=rgb(0.7, 0.7, 0.7, 0.5))
 regr_boot$coefficients
}

coeffs <- replicate(500, boot_regr(log(mpg) ~ log(weight), cars))
points(log(cars$weight), log(cars$mpg), col="pink", pch=19)
abline(a=mean(coeffs["(Intercept)",]), b=mean(coeffs["log(weight)",]), lwd=2)


```
# Mean Centering the Regression

```{r}
cars_log_regr_centering <- lm(scale(log.mpg., scale = F) ~ scale(log.cylinders., scale = F)+scale(log.displacement.,scale = F)+scale(log.horsepower., scale = F)+scale(log.weight., scale = F)+scale(log.acceleration., scale = F)+scale(model_year, scale = F)+factor(origin),data=cars_log)
summary(cars_log_regr_centering)
```

```
