---
title: "PLS_DML"
author: '109077446'
date: "4/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(seminr)
security_data_sem = read.csv("data/security_data_sem.csv")

sec_measurement_model <- constructs(
  composite("TRUST", multi_items('TRST',1:4)),
  composite("SEC", multi_items('PSEC',1:4)),
  composite("REP", multi_items('PREP',1:4)),
  composite("INV", multi_items('PINV',1:3)),
  composite("POL", multi_items('PPSS',1:3)),
  composite("FAML", single_item('FAML1'))
  # interaction_term(iv = 'REP', moderator = 'POL', method = orthogonal)
)
# 
# sec_structural_model <- relationships(
#   paths(from = c("REP","INV","POL", "FAML", "REP*POL"), to = "SEC"),
#   paths(from = "SEC", to = "TRUST")
#   
# )
# 
# sec_pls <- estimate_pls(data = security_data_sem, 
#                         measurement_model = sec_measurement_model, 
#                         structural_model = sec_structural_model)
# 
# sec_pls_sum <- summary(sec_pls)

# pls_variable <- as.data.frame(sec_pls_sum$composite_scores)
```

```{r}
sec_sm_full <- relationships(
  paths(from = c("REP","INV","POL", "FAML"),        to = "SEC"),
  paths(from = c("REP","INV","POL", "FAML", "SEC"), to = "TRUST")
)

sec_pls_full <- estimate_pls(data = security_data_sem, 
                             measurement_model = sec_measurement_model, 
                             structural_model = sec_sm_full)

plot(sec_pls_full)
```

# PLS Full Model TRUST ~ SEC + Z
```{r}

sec_pls_full_sum <- summary(sec_pls_full)

pls_variable <- as.data.frame(sec_pls_full_sum$composite_scores)

pls_theta <- sec_pls_full$path_coef["SEC", "TRUST"]
pls_theta
```

# OLS Regression TRUST ~ SEC
```{r}
# OLS regression without Z variables
ols_theta = coef(lm(TRUST ~ SEC, data = pls_variable))[2]
ols_theta
```

# Naive DML
```{r}
library(clusterGeneration)
library(mvtnorm)
library(randomForest)
 
set.seed(123) # = Seed for Replication = #
N = nrow(pls_variable)
 
z = pls_variable[,c("REP", "INV", "POL", "FAML")]
sec = pls_variable[,"SEC"]
trust = pls_variable[,"TRUST"]

# = Naive DML = #
# = Compute ghat = #
model = randomForest(as.matrix(z), trust)
G=predict(model,as.matrix(z))
# = Compute mhat = #
modeld=randomForest(as.matrix(z),sec)
M=predict(modeld,as.matrix(z))
# = compute vhat as the residuals of the second model = #
V=sec-M
# = Compute DML theta = #
theta_nv=mean(V*(trust-G))/mean(V*sec)
theta_nv
```
```{r}
## Naive DML function 
naive_dml <- function(cont_var,expl_var,outc_var){
  model = randomForest(as.matrix(cont_var), outc_var)
  G=predict(model,as.matrix(cont_var))
  modeld=randomForest(as.matrix(cont_var),expl_var)
  M=predict(modeld,as.matrix(cont_var))
  V=expl_var-M
  theta_nv=mean(V*(outc_var-G))/mean(V*expl_var)
  return(theta_nv)
}
```

```{r}
naive_dml(z, sec, trust)
```



# Cross-Fitting DML
```{r}
# = Cross-fitting DML = #
# = Split sample = #
I=sort(sample(1:N,N/2))
IC=setdiff(1:N,I)
# = compute ghat on both sample = #
z_mat = as.matrix(z)
model1=randomForest(as.matrix(z_mat[IC,]),trust[IC])
model2=randomForest(as.matrix(z_mat[I,]),trust[I])
G1=predict(model1,as.matrix(z_mat[I,]))
G2=predict(model2,as.matrix(z_mat[IC,]))

# = Compute mhat and vhat on both samples = #
modeld1=randomForest(as.matrix(z_mat[IC,]),sec[IC])
modeld2=randomForest(as.matrix(z_mat[I,]),sec[I])
M1=predict(modeld1,as.matrix(z_mat[I,]))
M2=predict(modeld2,as.matrix(z_mat[IC,]))
V1=sec[I]-M1
V2=sec[IC]-M2

# = Compute Cross-Fitting DML theta
theta1=mean(V1*(trust[I]-G1))/mean(V1*sec[I])
theta2=mean(V2*(trust[IC]-G2))/mean(V2*sec[IC])
theta_cf=mean(c(theta1,theta2))
theta_cf
```

```{r}
## Cross-fitting function
# e.g., cf_dml(z, sec, trust, bootstrap=TRUE)
cf_dml <- function(cont_var, expl_var, outc_var, bootstrap=FALSE){
  num_rows <- length(outc_var)
  
  if (bootstrap == TRUE) {
    # boot_i <- resample with replacement row indices
    boot_i <- sample(num_rows, size = num_rows, replace = TRUE)
    # I  <- # use first half of row bootstrapped indices
    I <- boot_i[1:(round(length(boot_i)/2))]
    # IC <- # use second half of row bootstrapped indices
    IC <- boot_i[(round(length(boot_i)/2)+1):length(boot_i)]
  } else {
    I  <- sort(sample(1:num_rows, num_rows/2)) # add randomness
    IC <- setdiff(1:num_rows, I)
  }
  browser()
  
  z_mat <- as.matrix(cont_var)
  model1 <- randomForest(as.matrix(z_mat[IC,]), outc_var[IC]) # some randomness
  model2 <- randomForest(as.matrix(z_mat[I,]), outc_var[I]) # some randomness
  G1 <- predict(model1, as.matrix(z_mat[I,]))
  G2 <- predict(model2, as.matrix(z_mat[IC,]))
  
  modeld1 <- randomForest(as.matrix(z_mat[IC,]), expl_var[IC]) # some randomness
  modeld2 <- randomForest(as.matrix(z_mat[I,]), expl_var[I]) # some randomness
  M1 <- predict(modeld1, as.matrix(z_mat[I,]))
  M2 <- predict(modeld2, as.matrix(z_mat[IC,]))
  V1 <- expl_var[I]-M1
  V2 <- expl_var[IC]-M2
  
  theta1 <- mean(V1*(outc_var[I]-G1))/mean(V1*expl_var[I])
  theta2 <- mean(V2*(outc_var[IC]-G2))/mean(V2*expl_var[IC])
  theta_cf <- mean(c(theta1,theta2))
  return(theta_cf)
}
```

```{r}
cf_dml(z, sec, trust)
```



# z: dataframe of control variables
# d: vector of explanatory variable of interest
# y: vector of outcome variable of interest
cf_dml <- function(z, d, y) {
  # ...
  # should return theta estimate
}

naive_dml_theta <- cf_dml(z, sec, trust)


```{r}
# naive_dml() and cf_dml() using the raw data items

z_item = security_data_sem[,c("PINV1","PINV2", "PINV3", "PPSS1", "PPSS2", "PPSS3", "FAML1","PREP1","PREP2","PREP3","PREP4")]

naive_dml(z_item, sec, trust)
```

```{r}
cf_dml(z_item, sec, trust)
```

# Monte Carlo CF-DML
 
```{r} 
library(parallel)

mc_cf_dml <- function(k=100, cont_var, expl_var, outc_var, bootstrap=FALSE) {
  cl <- parallel::makeCluster(detectCores())
  parallel::clusterExport(cl=cl, 
                          varlist=c("cont_var", "expl_var", "outc_var", "cf_dml"), 
                          envir=environment())
  clusterEvalQ(cl, {library(randomForest)})
  mc_results <- parallel::parSapply(cl, 1:k, 
                                    function(i) { cf_dml(cont_var, expl_var, outc_var, bootstrap=FALSE) }
  )
  stopCluster(cl)

  list(theta_replicates = mc_results,
       theta_mean = mean(mc_results))
}
```

# Using z constructs with MC-CF-DML
```{r}
set.seed(367387)
mc_cf_dml_construct <- mc_cf_dml(k=1000,z, sec, trust)
```

```{r}
plot(density(mc_cf_dml_construct$theta_replicates))
```

# Using z items with MC-CF-DML
```{r}
set.seed(367387)
mc_cf_dml_items <- mc_cf_dml(k=1000, z_item, sec, trust)
```

```{r}
plot(density(mc_cf_dml_items$theta_replicates))
```

## MC-CFDML Results

Means:
```{r}
mc_cf_dml_construct$theta_mean
mc_cf_dml_items$theta_mean
```

Standard Errors:
```{r}
sd(mc_cf_dml_construct$theta_replicates)
sd(mc_cf_dml_items$theta_replicates)
```


## BOOTSTRAPPED CF-DML
# Using z constructs with Bootstrapped MC-CF-DML
```{r}
set.seed(367387)
mc_cf_dml_const_boot <- mc_cf_dml(k=1000,z, sec, trust, bootstrap = TRUE)
```

```{r}
plot(density(mc_cf_dml_const_boot$theta_replicates))
```

# Using z items with Bootstrapped MC-CF-DML
```{r}
set.seed(367387)
mc_cf_dml_items_boot <- mc_cf_dml(k=1000, z_item, sec, trust, bootstrap = TRUE)
```

```{r}
plot(density(mc_cf_dml_items_boot$theta_replicates))
```
## Bootstrapped MC-CFDML Results

Means:
```{r}
mc_cf_dml_const_boot$theta_mean
mc_cf_dml_items_boot$theta_mean
```

Standard Errors:
```{r}
sd(mc_cf_dml_const_boot$theta_replicates)
sd(mc_cf_dml_items_boot$theta_replicates)
```

# TODO:

# MAYBE TODO LATER:
X. Let's re-estimate an indirect effect using CF_DML:
  a. get indirect effect and its CI
    - bootstrap sec_pls_full model using seminr::bootstrap_model() [let's call it boot_pls_full]
    - estimate the indirect effect of POL -> (SEC) -> TRUST
      seminr::specific_effect_significance(boot_pls_full, from = "POL", to = "TRUST", through = "SEC")
  b. 
X. Conduct CFDML/MC-CFDML/Boot-CFDML on another only items (not the SEC/TRUST constructs)
X. Repeat CFDML/MC-CFDML/Boot-CFDML on another dataset+model (where nonlinear effects are found to be present)

# DONE
1. Write naive_dml() and cf_dml() functions that we can reuse on new models --> DONE!
2. Use the raw data items of REP, INV, POL, FAML as "z" for naive_dml() and cf_dml() --> DONE!
Observations:
- the results of naive-DML are stable to 3rd decimal place -- we think that randomforest appoach introduces some randomness
- the results of CF-DML are not stable -- changes at 1st and 2nd decimal place -- we suspect the random index selection (cross-fitting) introduces much more randomness
3. To get a stable CF-DML estimate, run CF-DML 100 times and take average theta result
  a. Create mcCF-DML function (monte carlo CF-DML) -- it will call cf_dml() k number of times and return a list: vector of theta estimates; average theta
  b. Get a distribution of theta estimates
4. Run Montecarlo CFDML data
  a. research a bit about mc methods (take notes and citations) --> DONE!
  b. using z constructs (1000 iterations) --> DONE!
  c. using z items (1000 iterations) --> DONE!
  d. visualize distribution of both runs --> DONE!
  e. understand the difference in estimations --> DONE! (not much difference)
5. Run Bootstrapped CFDML --> DONE! (no differences from regular MC-CFDML)
  a. Run z-construct Bootstrapped MC-CFDML
  b. Run z-item Bootstrapped MC-CFDML
  c. Visualize results
  d. See Means and Standard Errors
