---
title: "PLS Bootstrapped"
author: '109077446'
date: "4/1/2022"
output: html_document
---

TODO:
1. Run Security PLS model --> DONE
  a. Make sure you can find actual values, fitted values and residuals from PLS
    - actual values: trust_actual_scores <- sec_pls_full$construct_scores[, "TRUST"]
    - fitted values:
      - fitted <- predict(sec_pls_full, security_data_sem)
      - trust_item_fitted_scores <- fitted$predicted_items[, 1:4]
      - we have to make the construct scores from the item data
      - trust_weights <- sec_pls_full$outer_weights[,"TRUST"][1:4]
      - trust_fitted_construct_scores <- trust_item_fitted_scores %*% trust_weights
      - trust_fitted_std_scores <- scale(trust_fitted_construct_scores)
    - trust_fitted_residuals <- trust_actual_scores - trust_fitted_std_scores
2. Try a residual bootstrap (scores) --> DONE
3. Try a wild bootstrap (scores) --> DONE
4. Try a residual bootstrap (items)
5. Try a wild bootstrap (items)

```{r}
library(seminr)
security_data_sem = read.csv("data/security_data_sem.csv")

sec_measurement_model <- constructs(
  composite("TRUST", multi_items('TRST',1:4)),
  composite("SEC", multi_items('PSEC',1:4)),
  composite("REP", multi_items('PREP',1:4)),
  composite("INV", multi_items('PINV',1:3)),
  composite("POL", multi_items('PPSS',1:3)),
  composite("FAML", single_item('FAML1'))
)

```

```{r}
sec_sm_full <- relationships(
  paths(from = c("REP","INV","POL", "FAML"),        to = "SEC"),
  paths(from = c("REP","INV","POL", "FAML", "SEC"), to = "TRUST")
)

sec_pls_full <- estimate_pls(data = security_data_sem, 
                             measurement_model = sec_measurement_model, 
                             structural_model = sec_sm_full)

plot(sec_pls_full)
```
## Ordinary non-parametric bootstrap
```{r}
ord_boot_pls <- bootstrap_model(sec_pls_full, nboot= 1000, cores = 2)
```
```{r}
summary(ord_boot_pls)
```






## Actual Values
```{r}
trust_actual_scores <- sec_pls_full$construct_scores[, "TRUST"]
```

## fitted values

```{r}
fitted <- predict(sec_pls_full, security_data_sem)
trust_item_fitted_scores <- fitted$predicted_items[, 1:4]
trust_weights <- sec_pls_full$outer_weights[,"TRUST"][1:4]
trust_fitted_construct_scores <- trust_item_fitted_scores %*% trust_weights
trust_fitted_std_scores <- scale(trust_fitted_construct_scores)

# SOUMYA TODO: verify/update procedure to get fitted construct scores
# scaled_predicted_items <- scale(fitted$predicted_items[, 1:4])
# fitted_construct_scores <- scaled_predicted_items %*% trust_weights
```


## Residual Value
```{r}
trust_fitted_residuals <- trust_actual_scores - trust_fitted_std_scores
```

## X variable scores
```{r}
trust_antecedent_scores <- as.data.frame(sec_pls_full$construct_scores[, 1:5])
```


## The Residual Bootstrap

```{r}
res_boot <- function(actual_scores,fitted_scores, residual_score, antecedent_scores) {
  # 2. Resample the residuals with replacement and obtain the bootstrapped residual vector resb
  resb <- sample(residual_score, length(residual_score), replace = TRUE)
  
  # 3. Obtain the bootstrapped dependent variable by multiplying the estimator(s) from (1) with the original regressors and adding the bootstrapped residual
  yb   <- fitted_scores  + resb
  
  # 4. Run the regression with the bootstrapped dependent variables and the original regressors
  regrb <- lm(yb ~ REP + INV + POL + FAML + SEC, data=antecedent_scores)
  
  regrb$coefficients
}
```

```{r}
set.seed(7893454)
sec_res_boot <- t(
  replicate(1000, 
            res_boot(trust_actual_scores, trust_fitted_std_scores, 
                     trust_fitted_residuals, trust_antecedent_scores))
  ) |> as.data.frame()
```

```{r}
plot(density(sec_res_boot$SEC))
```

## Wild Bootstrap 

```{r}
wild_boot <- function(actual_val, fit_val, res_val, ant_vals) {
  # sample_frame <- cbind(actual_val, fit_val, res_val, ant_vals)
  
  normal_vector <- rnorm(length(actual_val))
  y_b <- fit_val + res_val * normal_vector
  
  wild_regr <- lm(y_b ~ REP + INV + POL + FAML + SEC, data=ant_vals)
  # wild_regr <- lm(fit_val ~ y_b, data=sample_frame)
  
  wild_regr$coefficients
  #sample_frame
}
```

```{r}
set.seed(7893454)
sec_wild_boot <- t(
  replicate(1000, 
            wild_boot(trust_actual_scores, trust_fitted_std_scores, 
                      trust_fitted_residuals, trust_antecedent_scores))
  ) |> as.data.frame()
```

```{r}
plot(density(sec_wild_boot$SEC))
```


## ITEMS

```{r}
z_item2 <-  security_data_sem[,c("PINV1","PINV2", "PINV3", "PPSS1", "PPSS2", "PPSS3", "FAML1","PREP1","PREP2","PREP3","PREP4")]
```

## Actual Values
```{r}
item_actual_scores <- sec_pls_full$construct_scores[, "TRUST"]
```

## fitted values

```{r}
fitted <- predict(sec_pls_full, security_data_sem)
items_item_fitted_scores <- fitted$predicted_items[, 9:19]
items_weights_rep <- sec_pls_full$outer_weights[,"REP"][9:12]
items_weights_inv <- sec_pls_full$outer_weights[,"INV"][13:15]
items_weights_pol <- sec_pls_full$outer_weights[,"POL"][16:18]
items_weights_faml <- sec_pls_full$outer_weights[,"FAML"][19]
items_weights <- c(items_weights_rep,items_weights_inv,items_weights_pol,items_weights_faml)
items_fitted_construct_scores <- items_item_fitted_scores %*% items_weights
items_fitted_std_scores <- scale(items_fitted_construct_scores)

# SOUMYA TODO: verify/update procedure to get fitted construct scores
# scaled_predicted_items <- scale(fitted$predicted_items[, 1:4])
# fitted_construct_scores <- scaled_predicted_items %*% trust_weights
```


## Residual Value
```{r}
items_fitted_residuals <- item_actual_scores - items_fitted_std_scores
```

## X variable scores
```{r}
items_antecedent_scores <- as.data.frame(sec_pls_full$construct_scores[, 1:5])
```


## The Residual Bootstrap



```{r}
set.seed(7893454)
sec_res_boot <- t(
  replicate(1000, 
            res_boot(item_actual_scores, items_fitted_std_scores, 
                     items_fitted_residuals, items_antecedent_scores))
  ) |> as.data.frame()
```

```{r}
plot(density(sec_res_boot$SEC))
```